Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-07 numerical-particle.tex
Minor change to note that PotentialIterations is user-facing and add comment about MaximumParticleRefinementLevel.

>>>>

To avoid unphysical point-mass effects, \enzo\ provides a parameter that
governs the maximum level at which particles will be regarded at point masses.
At higher levels, contributions from particles to the gravitating mass field
will be smoothed over a spherical region centered at each particle's center.
